### 2020-05-30 writeup/transfer.tex
merge

\textbf{Implication 1.}
We use our tools to explain a key result of taskonomy \cite{ZSSGM18}, which shows that by learning from multiple related tasks, one can reduce the amount of labeled data from each task.
This is formalized by a metric called the data efficiency ratio as follows.

Given several tasks, let $\alpha^{\star}$ be the largest factors such that the total number of labeled datapoints needed for solving all tasks can be reduced by an $\alpha^{\star}$ factor (compared to training independently) while keeping the same performance.
%More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
For $i = 1, 2$, let $\hat{\beta}_i^{\MTL}(\alpha)$ denote the estimator trained using only $\alpha n_i$ datapoints from every task.
The data efficiency ratio is defined as
\[ \alpha^{\star} \define\argmin_{\alpha\in(0, 1)} ~~
		\te_1(\hat{\beta}_1^{\MTL}(\alpha)) + \te_2(\hat{\beta}_2^{\MTL}(\alpha))
		\le \te_1(\hat{\beta}_1^{\STL}) + \te_2(\hat{\beta}_2^{\STL}). \]
We quantify the data efficiency ratio of the isotropic model as follows.

\begin{proposition}[Labeled data efficiency]\label{prop_data_efficiency}
	In the isotropic model, assume that $\rho_1$ and $\rho_2$, $pd^2 < {8\sigma^2} /{(3 \rho)}$.
	Then the data efficiency ratio is at most $\frac{1}{2\rho} + \frac{\sigma^2}{2\sigma^2 - 3p d^2 \rho / 4}$.
\end{proposition}
The proof of Proposition \ref{prop_data_efficiency} can be found in Appendix \ref{app_proof_data}.

>>>>

\textbf{Implication 1.}
We use our tools to explain a key result of taskonomy \cite{ZSSGM18}, which shows that by learning from multiple related tasks, one can reduce the amount of labeled data from each task.
This is formalized as follows.

Given several tasks, let the data efficiency ratio be the largest factor $x$ such that the total number of labeled datapoints needed for solving all tasks can be reduced by $x$ while keeping the same performance compared to STL.
%More precisely, suppose we have $n_i$ datapoints for each task, for $i= 1, 2$.
For $i = 1, 2$, let $\hat{\beta}_i^{\MTL}(x)$ denote the estimator trained using only $\alpha n_i$ datapoints from every task.
The data efficiency ratio is defined as
\[ \argmin_{x\in(0, 1)} ~~
		\te_1(\hat{\beta}_1^{\MTL}(x)) + \te_2(\hat{\beta}_2^{\MTL}(x))
		\le \te_1(\hat{\beta}_1^{\STL}) + \te_2(\hat{\beta}_2^{\STL}). \]
We quantify the data efficiency ratio of the isotropic model as follows.

\begin{proposition}[Labeled data efficiency]\label{prop_data_efficiency}
	In the isotropic model, assume that $\rho_1,\rho_2 > 1$ and $\Psi(\beta_1, \beta_2) < \frac{2}{\rho_1} + \frac{2}{\rho_2}$.
	Let $$ the data efficiency ratio is bounded within
	$[ ]$
\end{proposition}
The proof of Proposition \ref{prop_data_efficiency} can be found in Appendix \ref{app_proof_data}.
